Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
on analyse sur des entiers Z et des reels

>>>>

The Lapack/Blas benchmarks are unusual compared to the other programs. These libraries perform matrix computations, using nested loops over indices; such programs are the prime target for polyhedral loop optimization techniques and it is therefore unsurprising that polyhedra perform very well over them.
